quicR: An R Package for Real-Time Quaking Induced Conversion (RT-QuIC) Assays

### 2025-01-03 man/manuscript/manuscript.qmd
Updated manuscript.

\begin{table}[ht]
\centering
\begin{tabular}{c|cccccccccccc}
   & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\ 
  \hline
  A & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
  B & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
  C & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
  D & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
  E & P & S12 & S13 & S14 & S15 & S16 & S17 & S18 & S19 & S20 & S21 & S22 \\ 
  F & P & S12 & S13 & S14 & S15 & S16 & S17 & S18 & S19 & S20 & S21 & S22 \\ 
  G & P & S12 & S13 & S14 & S15 & S16 & S17 & S18 & S19 & S20 & S21 & S22 \\ 
  H & P & S12 & S13 & S14 & S15 & S16 & S17 & S18 & S19 & S20 & S21 & S22 \\ 
   \hline
\end{tabular}
\end{table}

@@

### Maximum Slope
The Maximum Slope (MS) is calculated by the "calculate_MS" function. The data can be either raw or normalized. The function iterates through each row using a rolling window which can be adjusted (default value is 3). Given the window size, a linear model is developed on those data points, and the slope of the model is recorded. The MS is simply the largest slope value recorded.

```{r}
samples <- tabs$`Sample IDs` %>% na.omit()

@@

data.frame("Sample IDs" = samples) %>%
  mutate(
    # Maxpoint Ratio
    MPR = calculate_MPR(df_norm, start_col = 3, data_is_norm = TRUE),
    # Max Slope
    MS = calculate_MS(df_norm, data_is_norm = TRUE),
    # Time to Threshold
    TtT = calculate_TtT(df_norm, threshold = 2, start_col = 3),
    # Rate of Amyloid Formation
    RAF = ifelse(TtT == hours, 0, 1 / TtT),
    # Crossed threshold?
    crossed = TtT != hours
  ) %>%
  head(15) %>%
  kable(row.names = FALSE)
```

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{|c|cccccccccccc|}
  \hline
   & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\ 
  \hline
  A & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
  B & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
  C & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
  D & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
  E & P & S12 & S13 & S14 & S15 & S16 & S17 & S18 & S19 & S20 & S21 & S22 \\ 
  F & P & S12 & S13 & S14 & S15 & S16 & S17 & S18 & S19 & S20 & S21 & S22 \\ 
  G & P & S12 & S13 & S14 & S15 & S16 & S17 & S18 & S19 & S20 & S21 & S22 \\ 
  H & P & S12 & S13 & S14 & S15 & S16 & S17 & S18 & S19 & S20 & S21 & S22 \\ 
  \hline
\end{tabular}
\end{table}

@@

### Maximum Slope
The Maximum Slope (MS) is calculated by the "calculate_MS" function. The data can be either raw or normalized. The function iterates through each row using a rolling window which can be adjusted (default value is 3). Given the window size, the slope is calcualated based on the range of the window. The MS is simply the largest slope value recorded.

```{r}
samples <- tabs$`Sample IDs` %>% na.omit()
dilutions <- tabs$Dilutions %>% na.omit() %>% as.numeric()

@@

data.frame("Sample IDs" = samples) %>%
  mutate(
    Dilutions = -log10(dilutions),
    # Maxpoint Ratio
    MPR = calculate_MPR(df_norm, start_col = 3, data_is_norm = TRUE),
    # Max Slope
    MS = calculate_MS(df_norm, data_is_norm = TRUE),
    # Time to Threshold
    TtT = calculate_TtT(df_norm, threshold = 2, start_col = 3),
    # Rate of Amyloid Formation
    RAF = ifelse(TtT == hours, 0, 1 / TtT),
    # Crossed threshold?
    crossed = TtT != hours
  ) %>%
  head(15) %>%
  kable(row.names = FALSE)
```
